[dcpo_demsupport]

### 2020-06-07 paper/dcpo_demsupport.Rmd
exclude problematic WVS country-years; format data for Model 5; run Model 5; save output

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  tidyverse # data wrangling
)

@@

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

```{r replication-data-prep, eval=FALSE}
# claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv"),
#                                        file = "data/claassen_input_raw.csv")

claassen_input_raw <- read_csv("data/claassen_input_raw.csv") %>% 
  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1996 | year==2001)) |
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2005)) |
              (country=="India") |
              (country=="Pakistan" & (year==1996 | year==2001)) |
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001)))))

claassen_input <- DCPOtools::format_claassen(claassen_input_raw)

claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
                           data = claassen_input,
                           iter = 2000,
                           warmup = 1000,
                           chains = 4,
                           cores = 4,
                           thin = 2,
                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=15))

save(claassen_m5, file = "data/claassen_m5.RData")
```
